|

### 2022-12-12 r-report/Paper.Rmd
Updated figures

During the same period, China's emissions have risen rapidly. In 2004, the country surpassed the U.S. as the world's largest greenhouse gas emitter and is likely to retain that title for some time. In 2019, more than 25% of all global greenhouse gas emissions came from China, more than the U.S. and (at the time still) EU-28 combined (see Figure 1). As a consequence of this development, China's emissions profile changed dramatically: While the agricultural sector still accounted for a large share of emissions in the early 1970s, its contribution has been only marginal in recent years. Figure 2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector. More recently, transport sector emissions have picked up speed, likely reflecting the wealthy share of China’s citizens spending more money on individual (fossil-fuel based) modes of transport.

@@

Chinese carbon emissions growth was predominantly driven by its rapid economic development, which in turn caused the energy sector to grow too. Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 3). However, the growth of emissions has slowed in recent years, as energy intensity of GDP had started decreasing after the year 2005 and also carbon intensity of energy peaked in 2010 and has been slowly decreasing since. While for the first two decades of the 21st century carbon emissions growth rates were closely resembling the growth rates of GDP per capita, since 2010 the two numbers have decoupled. China’s immense expansion of renewable energy sources over the last years is likely an underlying driver of this trend, however, as we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e in 2019.

@@

```{r,fig.cap="Figure 1: Relative Emissions of the Top- 5 Polluters"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

```{r,fig.cap="Figure 2: Total Emissions, China by Sector - 1970-2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

```{r,fig.cap="Figure 3: Kaya Identity China - 2000 - 2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

Figure 4 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019. In those years, China’s GDP per capita was growing with a factor close to five, thereby being the strongest upward driver of emissions. GDP per capita increased almost in tandem with carbon emissions until 2010, in which a decoupling took place. Ever since, Chinese emission’s growth rates have been much slower than those of GDP per capita. This decoupling is likely due to the decreasing energy intensity of GDP and carbon intensity of energy at the same time. The energy intensity is the main counteracting factor on Chinese emissions and decreased constantly since 2005. The decreasing trend seemed to have already started in 2000 but had rebounded before 2005, which can be traced back to 2001, when China joined the WTO [@Zheng2020]. However, since 2010 the decrease has been significant, hence driving the reduction of overall emissions growth rate. Furthermore, one can see that carbon intensity of energy decreased since 2010 meaning that the amount of CO2 per unit of energy is decreasing. Nevertheless, the relationship remains a positive one. The decline of both the energy intensity and carbon intensity is likely due to economic efficiency improvements. Additionally, carbon intensity further declined because of increasing capacity additions of renewable energies (changes in the fossil share) and the reduced emission intensity of fossil fuels (changes in the fossil intensity, fuel switch) [@Zheng2020;@Peters2017]. Population changes only played a minor role but can be considered as a persistent upward driver of emissions.

@@

```{r,fig.cap="Figure 4: Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 5). In high-income countries, GDP per capita and population are increasing only at low levels (by roughly the factor 0.5 and 0.2 respectively). Carbon intensity and energy intensity are decreasing, keeping carbon emissions down. The carbon intensity is decreasing because of two factors: the fossil intensity and the fossil share. In contrast, in low-income countries, the growth of CO2 emissions is exceeding the growth of GDP per capita, both rising by a factor of 2.8 and 5 respectively over the observed time span. This is driven by a high and increasing carbon intensity. Furthermore, population growth plays an important role in this group, and can be considered a further driving factor of CO2 emissions. The only contrasting factor is the decreasing energy intensity. Comparing both groups of countries to China, one can resume that China’s development does not fit in either of the groups perfectly. Like before China’s Kaya decomposition shares similar characteristics as both groups: The small population growth resembles the trend of high-income countries, the dramatically decreasing energy resembles the trend of low-income countries. Considering lower-middle income countries, they seem to show upwards trends in any of the indicators except for energy intensity. In comparison, in upper-middle income countries carbon emissions and GDP per capita develop in tandem, while carbon intensity and energy intensity only fluctuate around zero in the years from 2000 to 2019.

```{r,fig.cap="Figure 5:Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before. We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings. China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 6 & 7. Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively. Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).

@@

```{r,fig.cap="Figure 6"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 7).

@@

```{r,fig.cap="Figure 7"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 8).

@@

```{r,fig.cap="Figure 8"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"

>>>>

During the same period, China's emissions have risen rapidly. In 2004, the country surpassed the U.S. as the world's largest greenhouse gas emitter and is likely to retain that title for some time. In 2019, more than 25% of all global greenhouse gas emissions came from China, more than the U.S. and (at the time still) EU-28 combined (see Figure 1.1). As a consequence of this development, China's emissions profile changed dramatically: While the agricultural sector still accounted for a large share of emissions in the early 1970s, its contribution has been only marginal in recent years. Figure 1.2 shows the large-scale industrialization of the country starting in the mid-1990s and the corresponding increase in emissions from the energy sector. More recently, transport sector emissions have picked up speed, likely reflecting the wealthy share of China’s citizens spending more money on individual (fossil-fuel based) modes of transport.

@@

Chinese carbon emissions growth was predominantly driven by its rapid economic development, which in turn caused the energy sector to grow too. Since the year 2000, China's GDP per capita has more than quadrupled, while carbon emissions have more than tripled in the same period (see Figure 1.3). However, the growth of emissions has slowed in recent years, as energy intensity of GDP had started decreasing after the year 2005 and also carbon intensity of energy peaked in 2010 and has been slowly decreasing since. While for the first two decades of the 21st century carbon emissions growth rates were closely resembling the growth rates of GDP per capita, since 2010 the two numbers have decoupled. China’s immense expansion of renewable energy sources over the last years is likely an underlying driver of this trend, however, as we have seen, Chinese annual emissions remain very high at 14.2 GtCO2e in 2019.

@@

```{r,fig.cap="Relative Emissions of the Top- 5 Polluters"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

```{r,fig.cap="Total Emissions, China by Sector - 1970-2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

```{r,fig.cap="Kaya Identity China - 2000 - 2019"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

Figure 3.1 displays China’s and developing and developed countries’ Kaya identities according to the IPCC classification in the Sixth Assessment Report from 2000 to 2019. In those years, China’s GDP per capita was growing with a factor close to five, thereby being the strongest upward driver of emissions. GDP per capita increased almost in tandem with carbon emissions until 2010, in which a decoupling took place. Ever since, Chinese emission’s growth rates have been much slower than those of GDP per capita. This decoupling is likely due to the decreasing energy intensity of GDP and carbon intensity of energy at the same time. The energy intensity is the main counteracting factor on Chinese emissions and decreased constantly since 2005. The decreasing trend seemed to have already started in 2000 but had rebounded before 2005, which can be traced back to 2001, when China joined the WTO [@Zheng2020]. However, since 2010 the decrease has been significant, hence driving the reduction of overall emissions growth rate. Furthermore, one can see that carbon intensity of energy decreased since 2010 meaning that the amount of CO2 per unit of energy is decreasing. Nevertheless, the relationship remains a positive one. The decline of both the energy intensity and carbon intensity is likely due to economic efficiency improvements. Additionally, carbon intensity further declined because of increasing capacity additions of renewable energies (changes in the fossil share) and the reduced emission intensity of fossil fuels (changes in the fossil intensity, fuel switch) [@Zheng2020;@Peters2017]. Population changes only played a minor role but can be considered as a persistent upward driver of emissions.

@@

```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Developed and Developing according to AR_6 Classification"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

Thus, in the next steps, the World Bank’s Income Classification Scheme will be used for comparison (Figure 3.2). In high-income countries, GDP per capita and population are increasing only at low levels (by roughly the factor 0.5 and 0.2 respectively). Carbon intensity and energy intensity are decreasing, keeping carbon emissions down. The carbon intensity is decreasing because of two factors: the fossil intensity and the fossil share. In contrast, in low-income countries, the growth of CO2 emissions is exceeding the growth of GDP per capita, both rising by a factor of 2.8 and 5 respectively over the observed time span. This is driven by a high and increasing carbon intensity. Furthermore, population growth plays an important role in this group, and can be considered a further driving factor of CO2 emissions. The only contrasting factor is the decreasing energy intensity. Comparing both groups of countries to China, one can resume that China’s development does not fit in either of the groups perfectly. Like before China’s Kaya decomposition shares similar characteristics as both groups: The small population growth resembles the trend of high-income countries, the dramatically decreasing energy resembles the trend of low-income countries. Considering lower-middle income countries, they seem to show upwards trends in any of the indicators except for energy intensity. In comparison, in upper-middle income countries carbon emissions and GDP per capita develop in tandem, while carbon intensity and energy intensity only fluctuate around zero in the years from 2000 to 2019.

```{r,fig.cap="Kaya Identities - 2000 - 2019| China vs. Income Levels"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

In this part, sector trends of different groups of countries will be considered using the same two categories of country groups as before. We take into account five sectors: energy, industry, transport, AFOLU (which in the EDGAR database only includes agricultural emissions), and buildings. China’s relative GHG emissions by sector are presented in a stacked bar plot in Figure 3.3 & 3.4 Most of China’s emissions in 2019 came from the energy and industry sector with 44% and 38% respectively. Only smaller shares are attributable to transport (6%), buildings (5%) and AFOLU (6%).

@@

```{r,fig.cap="Relative sector Emissions-2019| China vs. Developed vs. Developing"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

As before, to get a more granular view on the split of emissions by sector, the World Bank’s classification will be consulted (Figure 3.5).

@@

```{r,fig.cap="Relative sector Emissions - 2019| China vs. Income Levels"}
source('r-imports/init.R')
source('r-analysis/meta.R')

@@

As the stacked bar plot can only provide a snapshot in time and relative emissions only tell a limited story, we will in a next step compare China’s per capita emissions by sector over time from 1970 to 2019 to those of our four income determined country groups (Figure 3.6).

@@

```{r,fig.cap="1970-2019| China vs. Income Levels"}
YEAR_L = 1850
YEAR_U = 2060
GAS = "GHG"
